\appendix

\chapter{Best practices assessment} \label{appendix:practices}

Similarly to the approach of \cite{serban2020adoption}, participants are asked about their team's level of adoption of AI/ML deployment best practices. The questions come from the entries of Tables \ref{table:best-practices-1} and \ref{table:best-practices-2} where \textit{GreatAI} was determined to provide a support level of \textit{Fully automated}.

\textbf{How well did the previous AI deployment that you collaborated on implement the following best practices?} \textit{Each statement can be rated on a 5-point Likert scale or as ``Not applicable''.}

\begin{enumerate}
\item Write reusable scripts for data cleaning and merging
\item Make datasets available on shared infrastructure
\item Use versioning for data, model, configurations and training scripts
\item Continuously monitor the behaviour of deployed models
\item Log production predictions with the model's version and input data
\item Store models in a single format for ease of use
\item Equip with a web interface, package image, provide REST API
\item Provide simple API for serving batch and real-time requests
\item Integration with existing data infrastructure
\item Querying, visualising and understanding metrics and event logging
\item Allow experimentation with the inference code
\item Keep the model and its documentation together
\item Parallelise feature extraction
\item Cache predictions
\item Allow robustly composing inference functions
\end{enumerate}

\chapter{TAM questionnaire} \label{appendix:questions}

Following the methodology for the parsimonious technology acceptance model of Wu et al. \cite{wu2011user}, each statement can be rated on a 7-point Likert scale.

\paragraph{Perceived usefulness (PU)}
\begin{enumerate}
 \item I believe the use of \textit{GreatAI} improves the quality of AI deployments.
 \item I believe the use of \textit{GreatAI} would increase my productivity.
 \item I believe the use of \textit{GreatAI} can lead to robust and trustworthy deployments.
 \item Overall, I found \textit{GreatAI} useful when working with AI.
\end{enumerate}

\paragraph{Perceived ease of use (PEOU)}
\begin{enumerate}
 \item I found the  \textit{GreatAI} easy to learn.
 \item I found it is easy to employ \textit{GreatAI} in practice.
 \item I found it is easy to integrate \textit{GreatAI} into an existing project.
 \item Overall, I found \textit{GreatAI} easy to use.
\end{enumerate}

\paragraph{Intention to use (ITU)}
\begin{enumerate}
 \item Assuming \textit{GreatAI} is applicable to my task, I predict that I will use it on a regular basis in the future.
 \item Overall, I intend to use the \textit{GreatAI} in my personal or professional projects.
\end{enumerate}

